From centralized certification systems to more internet-like ones

### 2015-12-26 paper.tex
All done !

Going deeper with user validation : DN scheme based on X.500 Recomendation, but it is not completly defined, and will (in 1998) probably not be. Also, X509 certification depends on many others such as ISO, ANSI, ITU and IETF. Thus lead to a lack of harmonization.
Plus, there is a big problem with CPS (Certification Practice Statements), that also can be seen such as flexibility (for pros), because each CA answer specific needs, so no harmonization again.

Also, regarrding to the law, CAs deny all leak of information from themselves.

@@

@@

>>>>

There is a big problem with CPS (Certification Practice Statements), that can be seen such as flexibility (for pros), because each CA answer specific needs, so that is a sort of lack of harmonization.

Also, regarding to the law, CAs deny all leak of information from themselves \cite{gerck1998overview}.

@@

\section{Conclusion}
\label{conclusion}

Although the great need to replace the PKIX security model\footnote{X.509 and CAs}, none of those presented below may be valid, or well tested to be implemented in a large scale (world wide).

Therefor, the best model may be the sovereign keys system associated with a DANE control of domain control certification, as soon as security problems will be fixed in DANE with DNSSEC.\\

Otherwise, another point of view that need to be discussed, is the economic impact on such revolution: compagnies like VeriSign\footnote{www.verisign.com} or GeoTrust\footnote{www.geotrust.com} may face bankruptcy with the removal of all CAs. Knowing taht hey are big deciders in the internet activity, they detain a great lever on governements (because money leads capitalism), to stop or at least slow down the process of deployement of a new certification system.

In general, to fit the Internet, experience has show us that we need to develop systems that are the most distributed as possible, like the internet paradigm.

\pagebreak

@@

\bibitem{mf2011} Maury, Florian. "La fin annoncée des autorités de certification? Alternatives: TOFU, Convergence, CATA, Clés souveraines, DANE." Convergence 10 (2011): 509.

\bibitem{correia2015dns} Correia, Miguel Medeiros, and Mustafa Tok. DNS-based Authentication of Named Entities (DANE). Technical report, Universidade do Porto, 2011–2012, 2015.
